The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multi-Phase Forest Inventories

### 2017-09-19 rnw/Main structure and modules of the Package.Rnw
update Andreas 19.09.2017(1)
Infinite population approach.

Lets assume that the spatial distribution of a target variable (e.g. the timber volume) over the forest area is determined by a mathematical continuous function. The \textit{total} of the target variable $Y$ (e.g. the total timber volume of the forest) consequently is the integral of that function, in other words: the volume that expands under the surface of that function (Figure \ref{fig:inf_pop_apr}). We can thus reconsider our task of estimating e.g. the true timber volume of a forest as "estimating the integral of the unknown function that determines the timber volume distribution over our forest". From this perspective, the challenging part of an inventory is that the form of this function, and thus $Y$, is unknown. Theoretically, we still could get $Y$ by observing the function value $Y(x)$, called the \textit{local density}, at each possible point $x$ over the function plain (i.e. the forest area) and sum those obervations up. However, we see at the first spot that this is impossible, because the number of function values $Y(x)$ and thus the number of possible sample points $x$ is $infinite$. So the only thing we can do is to get a sample of $Y(x)$ to \textit{estimate} $Y$ by $\hat{Y}$. Since we thereby sample from an infinite population of sample points, and thus function values, this approach is consequently called the \textit{infinite population approach}. All estimators included in the \proglang{R} package \pkg{forestinventory} basically rest upon these theoretical thoughts. In practice, the value of $Y(x)$ is determined by measuring sample trees that lie within a circle (called sample plot) around the sample point $x$ located in the forest area, and aggregating their individual characteristics (e.g. their individual timber volumes). However, a key point to understand is that in the infinite population approach, a local density value $Y(x)$ has \textit{no spatial association}. Even if we use a spatial unit to calculate $Y(x)$, its value solely corresponds to the sample point $x$, which constitutes the sample unit. This has some obvious practical advantages over the finite population approach, where the sample units actually are cirular or rectangular plots. One is the impossibility of a perfect tesselation of an amorphous forest area by any kind of plot-shape, and hence, the population in the finite approach is, strictly speaking, not defined. The consideration of an underlying infinite population of sample points will also play an important role when incorporating auxiliary information in the frame of two- and three-phase estimation methods.

\begin{figure}[htb]
\centering
\resizebox{0.5\hsize}{!}{\includegraphics{fig/OnePhase.png}}
\caption{Visualization of the infinite population approach. The spatial distribution of the target variable $Y$ is determined by a continous function (green plain) from which 
only a sample of function values $Y(x)$ (dots on the plain) is known from a terrestrial survey.}
\label{fig:inf_pop_apr}
\end{figure}

>>>>

Most forest inventories typically follow a procedure that involves randomly selecting points in the forest area defined by GPS coordinates to which inventorists are sent. At these points, the inventorist demarcates a sample plot, possibly with the help of an inclusion circle that indicates which trees above a certain threshold are to be selected for measurement. These measurements are then converted into local plot densities (e.g. the timber density in $\frac{m^3}{ha}$) before the desired estimator is applied.  The \pkg{forestinventory} package bridges this common inventory paradigm to the mathematics of the estimation process using what is called the \textit{infinite population approach}.  In this approach the sampling units are \textit{points} each of which has a local density that exists but might remain unobserved if that point was not selected in our inventory's sample. For the sake of argument, imagine that the local density for every point in the forested area was somehow known and we could visualize the spatial distribution of the local density function of a target variable (e.g. the timber volume) for the entire forest area (Figure \ref{fig:inf_pop_apr}). The \textit{population total} of the target variable (e.g. the total timber volume of the forest) is mathematically equivalent to the integral of that density function, which defines the volume under the green surface in (Figure \ref{fig:inf_pop_apr}). Clearly, evaluating the local densities for every one of the infinite point so that we can add them up is impossible. Thus, in the infinite population approach we are essentially approximating the integral of this unobserved density surface numerically by sampling directly from the surface with our terrestrial inventory sample. This is why the infinite population approach is also called the \textit{Monte-Carlo approach}.

All estimators included in the \pkg{forestinventory} package basically rest upon these theoretical thoughts. The motivation for this decision was that no bothersome spatial correlations need to be considered as would be the case with geostatisical methods since we assume that the inventory points are selected uniformly and independently, i.e. the infinite analogy for simple random sampling. Furthermore, points can perfectly fill up any forest area with any amorphous shape, which is not possible if one were to use the \textit{finite populatoin approach} where the sampling plot defined around the point is considered the sampling unit.  However, this has the disadvatage that circles don't tesselate perfectly and polygons will inevitably distort and pixelate the forest boundary.  In practice, the population of sampling units in the finite approach will almost never perfectly cover the forests.  We also want to emphasize that the consideration of an underlying infinite population of sample points will also play an important role when incorporating auxiliary information in the frame of two- and three-phase estimation methods.

\begin{figure}[htb]
\centering
\resizebox{0.5\hsize}{!}{\includegraphics{fig/OnePhase.png}}
\caption{Visualization of the infinite population approach. The spatial distribution of a hypothetical density function for every point in a forested area is represented as wavy green surface.  Sample plots (grean circles) inform the inventorist of the value of the density function at that point.}
\label{fig:inf_pop_apr}
\end{figure}
